# Reproducible Research: Peer Assessment 1

## Loading and preprocessing the data

```{r}
fzip = "repdata-data-activity/activity.csv"
stepdat <- read.table(fzip, sep=",", stringsAsFactors=FALSE, as.is=TRUE, header=TRUE, na.strings="NA")
stepdat$day <- as.Date(stepdat$date, "%Y-%m-%d")
stepdat.no_na <- data[!is.na(stepdat$steps),]
steps.per.day=xtabs(steps ~ day, data=stepdat.no_na)
```


## What is mean total number of steps taken per day?

### Make a histogram of the total number of steps taken each day
```{r}
hist(steps.per.day, breaks=11, xlab="steps per day", main="Distribution of Number of Steps Taken per Day")
```

### Calculate and report the mean and median total number of steps taken per day
```{r}
mean(as.vector(steps.per.day)) # [1] 10766.19
median(as.vector(steps.per.day)) # [1] 10765
```

## What is the average daily activity pattern?

### Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r}
library(plyr)
steps.per.day.mean <- ddply(stepdat.no_na, .(interval), summarize, avg=mean(steps))
plot(steps.per.day.mean$interval, steps.per.day.mean$avg, type="l", 
    xlab="Interval (5 minute increment)",
    ylab="Average Number of Steps",
    main="Average Number of Steps per Day")
```
### Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
steps.per.day.mean[steps.per.day.mean$avg==max(steps.per.day.mean$avg),1] # [1] 835
```


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
